---
title: "Data_extracting"
author: "Min-Yang Lee"
date: "`r format(Sys.time(), '%B %d, %Y')`" 
output:
  pdf_document: default
  html_document: default
urlcolor: blue
---

<!-- 
This is the markdown document used to extract the DMIS data and save it to a flat file. Extracting the DMIS data takes a long time. 
-->
# Project setup
here(), load libraries, and set a data vintage.

```{r setup, include=TRUE, echo=TRUE, results=FALSE}
# Set Path
here::i_am("R_code/DMIS_2022_extracting.rmd")

# Please ensure you have the proper packages installed with (install.packages()) or a request to ITD if any libaries do not load.  
library("here")
library("RODBC")
library("readxl")
library("offshoreWind")
library("tidyverse")

vintage_string<-Sys.Date()
vintage_string<-gsub("-","_",vintage_string)

dmis_savename<-paste0("APSD_WIND_TEST_",vintage_string,".Rds")

# You might want to run this code, but not extract and save any data. Set this switch to FALSE to do so.
extract_switch=TRUE
```

# Organization


```{r folder_create, include=TRUE, echo=FALSE, results=FALSE}
# You only need to run this once, but nothing bad will happen if you keep include=TRUE.
# Set up some folders
dir.create(here("raw_data"), showWarnings="FALSE")
```

## Read in oracle passwords and set network directory
This is a block of code where we set up the oracle passwords and make R aware of folders on the network.

```{r oracle_connections, echo=TRUE, results=FALSE}
source(here("R_code","project_logistics","R_credentials_RODBC.R"))

# Set the network_location_desktop and network_location_remote variables somewhere OUTSIDE of this code.  The best place to do this is in the .Rprofile or .Renviron files that are in your root directory.  

#Comment one of these out, depending on whether you are running this code on a server or locally (with VPN) 
net<-network_location_desktop
net<-network_location_remote

```



# Purpose

This code extracts DMIS data. 

##  DMIS



# Load Offshore Wind Tool Data sets 

The frozen DMIS table from the offshoreWind project (APSD_DMIS_2) is the base dataset for the analysis.  The DMIS data are formed by combining many datasets, including VTR and Dealer.  In brief, the APSD_DMIS_2 dataset contains a mix of trip attributes (port, date),  sub-trip attributes (gear, location) , and catch outcomes (species, pounds, landed, dollar).  You can read more about DMIS [here](https://github.com/NEFSC/READ-SSB-Lee-metadata/blob/master/DMIS.md).


To get a more up-to-date version of this data, we can do:
```{r DMIS_live_query, echo=TRUE, eval=extract_switch}
oracle_server = "sole"
ODBC.CONNECTION <- RODBC::odbcConnect(dsn=oracle_server, uid=oracle_username, pwd=oracle_password, believeNRows=FALSE)
#SUBSET.QUERY = paste ("select * FROM APSD.DMIS_WIND_TEST@garfo_nefsc where YEAR=2021")
CURRENT.QUERY = paste ("select * FROM APSD.DMIS_WIND_TEST@garfo_nefsc")
APSD_DMIS_WIND_TEST = sqlQuery(ODBC.CONNECTION, CURRENT.QUERY)
odbcCloseAll()
summary(APSD_DMIS_WIND_TEST)
```


```{r WIND_TEST_tidyups, echo=TRUE, results=FALSE,eval=extract_switch}
APSD_DMIS_WIND_TEST <- APSD_DMIS_WIND_TEST %>%
  mutate("NESPP3" = as.character(NESPP3)) %>%
  select(-DEALER_RPT_ID)

```

```{r save_dmis_flat, echo=TRUE}
saveRDS(APSD_DMIS_WIND_TEST, file=here("raw_data",dmis_savename))
```



```{r check columns, echo=TRUE, results=TRUE,eval=T}
#load(file.path(offshoreWind_directory, "APSD_DMIS_2.rda"))
APSD_DMIS_WIND_TEST<-readRDS(file=here("raw_data",dmis_savename))
APSD_DMIS <- as_tibble(offshoreWind::APSD_DMIS_2) # load from data/ folder

# List the column names
sort(colnames(APSD_DMIS_WIND_TEST))
sort(colnames(APSD_DMIS))

```
The original has a SPPNAME, but this doesn't exist in WIND_TEST. Not a problem, it looks like it gets dropped.





# R Session Information
```{r session_info, include=TRUE, echo=TRUE, results=TRUE, eval=TRUE}
sessionInfo()
Sys.Date()

```
This may be useful for diagnosing and troubleshooting one day.


